Predicting sales of newly published books

### 2015-08-24 paper.tex
Fixing typos and grammar errors and added coments for @pacastillo

%% Many companies must face, as one of the most difficult tasks to
%% accomplish, new product sales estimation, since in many cases no
%% historical data to serve as guide is available. 
%% Moreover, some of them lack the knowledge about forecasting methods
%% and they can only make decisions based on the expert sales
  %% managers. 
% Eliminado esto.
When a new book is published the publishing house faces the problem of
how many books should be printed. Printing too many is the main issue,
since it implies a loss of investment due to inventory excess. That is
why in this paper we are tackling the problem or predicting sales to 
print the right amount of books, doing so even before the book has
reached shelves, which is when printing occurs. 
%Thus, making inaccurate predictions may lead to erroneous decisions that result in excess production that will not be sold, or even to a production deficit.
%That is the publishing roll problem, in which publishing companies must estimate the number of volumes printed, taking care not to print more than they actually end up selling. Thus, an automatic prediction of book sales to estimate the publishing roll would be helpful for publishers.
% In the literature, different methods of sales prediction, mainly for
% the fashion industry are proposed. 
% Esto no pega nada en el abstract - JJ
%In these works, when sales are stable with a clear trend over time, the classical methods are a good choice. 
%However, in the case of new products, such as a new book publishing, classical methods do not work properly.
%In this paper, a rule-based decision method is proposed to address the
%problem of predicting the publishing roll.  
% It's not proposed. It just obtained the best result with WEKA. - JJ 
% Publishing roll? ¿Qué es? - JJ
%[Pedro] en la traducción de términos Antonio propone traducirlo como "print run". Lo pongo así.
In this paper, which works with data on published books for several years in 
Spain, we first apply a data visualization and preprocessing strategy to find
out what are the relevant variables in the prediction of sales, and
then use standard data mining software to predict sales, and from them
deduce print-run, based on those variables. Our work discovers which
are the most relevant variables when predicting sales, and is
eventually able to predict sales with remarkable accuracy. In fact,
this method has been validated by the company that provided the data 
and incorporated in a business intelligence tool for publishing houses,
since the obtained models provide information on the decision process and
does not require human intervention either for the operation or for
interpretation.
\end{abstract}

@@

However, accurately using a predictive tool is a difficult task as
book sales are influenced by various factors that make
them fluctuate and usually they might be not controllable and
sometimes unknown. 
Some have to do with decisions on purchases, others with freight
traffic, and others with the distribution strategy \cite{Little1998}.

@@

The rest of this paper is structured as follows: next, 
Section \ref{sec:soa} presents a comprehensive review of the
approaches found in the bibliography related to the prediction of
sales from product characteristics. 
Then, Section \ref{sec:problem} describes the 
problem of how many books should be printed when a new book is published, 
        % no es el problema de publicación, es el problema de venta
        % de libros sin publicar. Habrá que buscar un nombre - JJ
        %[Pedro] cierto, lo cambio, aunque me ha quedado un nombre muy largo  :)
 followed by Section \ref{sec:methodology} where the
experimental setup and the methodology considered in the study is
presented.  
Section \ref{sec:experiments} reports and analyzes the obtained results with a 
real data set. Finally, conclusions and future work are presented in Section
\ref{sec:conclusionsAndFutureWork}.

%********************************************************************************
\section{Sales forecasting. State of the art}
\label{sec:soa}

@@

Specifically, using time series prediction methods \cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990} 
is perhaps the most used technique to tackle the sales forecasting problems, 
the efficiency of these techniques depends largely on the field of application 
and the problem data as they require a large amount of data for predicting 
sales of new products are not the most suitable for this task \cite{ChingChin2010}.

@@

  %[pedro] sobre la industria editorial no hay trabajos sobre predicción de ventas.
  % Lo habitual ha sido usar el conocimiento de expertos para realizar predicciones 
  %  o aconsejar acerca de la cantidad de libros a imprimir.
  % Lo más parecido que he encontrado son dos trabajos (uno en realidad) de Moon et al. 
  %  sobre "Use Blog Information As Book Sales Prediction":
  %     Moon2010ICSSSM
  %     Moon2010ICEC
Recently, some works propose \cite{Moon2010ICSSSM,Moon2010ICEC} analyzing 
relationships between on-line information and book sales.
Specifically, authors propose using the number of blog references as an indicator 
of book sales.
Different sales patterns are observed by analyzing data obtained.
In any case, in this research, historical data from published books is used, 
and the proposed methodology can not be usable in the problem of unpublished-books 
sales prediction.

@@

Some authors have faced the problem of forecasting sales of new products using 
different data mining methods \cite{Hammond1990,Chang2009,ChingChin2010,Thomassey2012,Xia2012}. 
Thomassey et al \cite{SThomassey2014} propose using a clustering method and 
decision trees for sales forecasting in textile-appared fashion industry, 
a very similar issue to the new book publishing problem.
The same problem was previously faced by Xia et al \cite{Xia2012} using a 
forecasting method based on extreme learning machine with adaptive metrics of inputs.
Complexity of this problem is due to the lack of historical data, short lifetime 
of the large number of items, and due to the influence of variables such as 
promotions, fashions, or economic environment \cite{Thomassey2012,Xia2012,SThomassey2014}.

  %[Pedro] otro caso muy similar es el paper de ChingChin2010 sobre:
  % New tea product
  % New cosmetic product
  % New soft drink product
In \cite{ChingChin2010}, a decision-support system for new product sales 
forecasting is proposed to solve three real-world sales forecasting problems 
involving new tea, cosmetic, and soft drink products taking into account 
quantitative variables. 
In this study, it is assumed that products are classified based on their sales 
pattern so that products in the same class would have similar sales pattern.
However, as the authors state, proposed system can not deal with qualitative 
date related to the products, and even more real-world cases, such as consumer 
electronics and fashion products, should be examined, as these industries 
introduce new products every season.

  %[Pedro] otro caso a comentar es el paper de Chang2009 sobre: 
  % sales forecasting in printed circuit board industry.
In those cases where historical data is available, classical time series 
forecasting methods can be applied, such as in \cite{Chang2009}, where a hybrid 
model integrating K-mean and fuzzy neural networks to forecast the future sales 
of a printed circuit board is proposed.
A similar method is proposed by Chern et al \cite{Chern2015}, who analyze 
historical data along online reviews, reviewer characteristics and review 
influences to understand how electronic word-of-mouth affects product sales. 
Proposed method is suitable in those sales forecasting problems with abundant 
online reviews and historical data.

@@

In the case of already published books, available historical data might help 
to generate predictive models.
However, in the case of new books there is no historical data to define patterns, 
and only some descriptive data about the new book is available.
In these cases not any forecasting method can be used\cite{Madsen2008,ChernWSF15}.

An additional issue is the dificulty to compare our model with classical 
forecasting methods, such as time series prediction methods, since books 
do not have specific sales time series.

Throughout this research we collaborated with the company Trevenque Editorial, %\footnote{{\tt http://editorial.trevenque.es}}, 
a company that provides management systems and services for libraries, publishers 
and distributors.

Trevenque company, whose expert manager advised this research, provided 
the initial data set consisting of 3159 books.
In this data set, descriptive information for each book includes price, 
selling points, matter, publisher, sales, returns, among other information.
Table \ref{tabla:paramsOrig50} shows the original set of parameters describing 
each book.

@@

There are several issues inherent to the problem of predicting sales of new 
products: the limitation on the amount of data available, the application of 
different methods and choose the most suitable of them.
In addition, there is no a standard methodology to solve the general problem 
of sales forecasting.
Usually, a preliminary analysis of the data is carried out to eliminate those 
variables that describe the product but do not provide useful information during 
the prediction process.

@@

Thus, in this study there are three main stages (see Figure \ref{fig:stages} 
for details): 
\begin{itemize}

@@

  \item  Then, several forecasting methods has to be tested. In this stage 
  different forecasting methods are used to obtain sales forecasts from the 
  data provided.

@@

Finally, in the literature different error measures can be found to report 
the results obtained using the prediction methods \cite{ChingChin2010,Madsen2008}. 
Those error measurements are also called error functions or cost functions. 
%One of the most commonly used is the mean absolute error (see equation \ref{eq:MAE}).
In any case, we recommend using widely accepted standard 
equations\footnote{http://www.gepsoft.com/gxpt4kb/Chapter10/Section3/Introduction.htm} 
in order to compare obtained results with those presented in other research 
papers using other methods.
That is why different standard error measurements (Equations \ref{eq:MAE} to \ref{eq:RRSE}), 
implemented in tools like Weka\footnote{http://wiki.pentaho.com/display/DATAMINING} \cite{Witten2011} 
or R\footnote{https://www.otexts.org/fpp/2/5} \cite{Hyndman2013}, are proposed.

Specifically, in order to compute the forecasting errors of the different methods, 
Mean absolute error (MAE), Root mean squared error (RMSE), Relative absolute 
error (RAE) and Root relative squared error (RRSE) have been selected:

@@

This method is usually applied to analyze data as similar items tend to be 
mapped close together, while those items dissimilar, are mapped apart.
Also, the SOM graph represents and highlight very clearly those regions (clusters) 
with high training sample concentration and fewer where the samples are scarce.

As stated in Section \ref{sec:problem}, an expert sales manager colaborated in 
this research in the stage of data analysis. Thus, the process was as follows:
\begin{itemize}
  \item First, the expert removed superfluous variables, and dimensionality was 
  reduced from 50 to 43 inputs.
  \item Then, the expert, using his knowledge and the information obtained 
  analyzing the SOM results, removed some inputs, reducing the number of 
  variables describing a book from 43 to 13.
  \item The company asked to include the information about \emph{editorial} 
  and \emph{materia}. Thus, in a new iteration, taking into account the expert's 
  advice and the información obtained analyzing the SOM results, the number of 
  inputs was decreased to 7.
  \item In a third step, several forecasting methods were used on the obtained 
  dataset, and the best was choosen to obtain an accurate predicting model.
  \item Finally, some information about the new book, such as \emph{author}, 
  although not included in the obtained models, was taken into account by 
  the expert sales manager to modify the forecasted results. 
\end{itemize}

@@

More specifically, in a first step, the expert analyzed the 50 input variables 
describing each book to remove those that were suplerfuas.
Table \ref{tabla:params43} shows the set of variables describing a book 
(43 total inputs) that the expert manager determined as non-superfluous or 
non-redundant.

@@

Then, after analizyng the original dataset using the SOM to select the best 
variables to be considered, and taking into account the knowledge of the company 
experienced manager, 13 inputs were considered. 
Figure \ref{fig:som43} shows the initial analisys of dataset using the total 
of 43 descriptive inputs per book.
Table \ref{tabla:params13} shows the set of variables describing a book after 
the second analisys.
	% esta gráfica no aporta nada, ni la siguiente tampoco. No se puede
	% colocar en un trabajo en revista  cómo ha ido el entrenamiento, sino
	% datos serios de análisis estadístico de las variables. 
	% [Pedro] sí, estoy de acuerdo. Esto va con el ISSUE #6
\begin{figure}[!h] 
\begin{center}
\begin{tabular}{c}
  \epsfig{file=som43vars.eps,width=11cm} \\
  \epsfig{file=som43umatrix.eps,width=5cm}
\end{tabular}
\caption{\small{Initial data analysis, using 43 descriptive variables per book, 
using SOM.}}
	% Cojollos, ¿qué trabajo os cuesta poner esto en inglés directamente? - JJ
	% [Pedro] sí, si estoy de acuerdo... hay días que me "sale" el texto en inglés,
	% pero hay días que soltar la parrafada en español me resulta más fácil    :/
        % Sería más bien exploratory data analysis o data visualization. 
        % Un gráfico no es un análisis. Y pon las cosas cortas en inglés, hombre - JJ
\label{fig:som43}
\end{center}
\end{figure}

@@

Finally, after analizyng the dataset with 13 descriptive inputs per
book, and paying attention to the company experienced manager's
recommendations, 7 inputs were considered; specifically, variables
\emph{EDITORIAL} and \emph{MATTER} were included, while
\emph{TOTAL DEVOLUTIONS, REPRINTS, TOTAL SELLING POINTS FIRST YEAR,
  NUMBER OF REPRINTS, TOTAL DEVOLUTIONS FIRT YEAR, TOTAL DISTRIBUTED FIRST YEAR,
  WEEKS ON SALE, PRINT-RUN} were discarded.  
	% Hay que aportar datos de por qué se hizo esto. ¿Análisis de planos?
	% ¿Análisis de varianza? - jj
	% [Pedro] En cuanto estén los SOM definitivos lo añadimos. Está relacionado con el ISSUE #6
Figure \ref{fig:som13} shows the initial analisys of dataset using the SOM on 
the total of 13 descriptive inputs per book.
This, along with the expert manager knowledge determined the final 7 inputs 
to be considered.
Table \ref{tabla:params7} shows the final set of variables describing a book, 
taking into account the company experienced manager knowledge.

\begin{figure}[!h] 
\begin{center}
\begin{tabular}{c}
  \epsfig{file=som13vars.eps,width=11cm} \\
  \epsfig{file=som13umatrix.eps,width=5cm}
\end{tabular}
\caption{\small{Análisis de los datos iniciales, usando 13 variables
    descriptivas por libro, utilizando el SOM.}}
% describir de forma más precisa: visualización usando UMatrix de... - JJ
% ¡y usar nombres en inglés para las variables! - JJ
%[pedro] es el siguiente arreglo que le haré mañana al paper    ;)
\label{fig:som13}
\end{center}
\end{figure}

@@

However, as in the case of new books only some descriptive data is available 
(compared to those cases in which historical data on sales of published books 
is available), not all forecasting methods can be used in this specific problem.

Thus, in this research five forecasting methods, based on the literature 
review in the introduction 
\cite{Madsen2008,ChingChin2010,Thomassey2012,Xia2012,SThomassey2014}, have been used. 
Well known forecasting methods implemented in the Weka tool
\cite{Hall2009,Witten2011} have been choosen, as these methods are
widely known, and could be very helpful for practitioners to reproduce
experiments and even to solve similar sales prediction problems using
these methods. % eliminado el pie de página, es mejor usar referencias - JJ

Specifically, following forecasting methods are proposed:
\begin{itemize}

@@

 % weka.classifiers.functions.SMOreg
 %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/SMOreg.html
 \item \emph{Support Vector Machine for Regression (SVM)}:
Support vector machine (SVM) \cite{Cortes1995,Shevade1999} method is based on  
statistical learning theory and has succesfully used in classification and  
regression problems \cite{Cao2003,Jari2008}.

In classification problems the algorithm searchs for an optimal hyperplane 
that separates two classes, maximizing the margin between two classes. 
In the case of regression the algorithm chooses a hyperplane close to as many 
of the data points as possible, minimizing the sum of the distances from 
the data points to the hyperplane. 
In both cases, the hyperplane is defined by a subset of training set samples 
(called support vectors).
%This method works well even if the space is highly dimensional and the problem is not linearly separable.

 % weka.classifiers.lazy.IBk 
 %		http://weka.sourceforge.net/doc.dev/weka/classifiers/lazy/IBk.html
 \item \emph{k-Nearest Neighbours (kNN)}: 
The kNN \cite{Aha1991,Mitchell1997} method is an instance-based classifier in 
wich the unknown instances are classified by relating them to the known 
instances using a distance measurement/function (Euclidean, Minkowsky or minimax).

@@

The classification algorithm locates the nearest neighbour in instance space and 
asigns the class of that neighbour to the unknown instance.
In order to improve the robustness of the model, several neighbours can be 
located, assigning the resulting class to an unclassified vector using the 
closest k vectors found in the training set by majority vote.

@@

This kind of artificial neural network is trained using a supervised learning 
technique called back-propagation.
This training method was developed independly by Werbos \cite{Werbos1974}, 
Parker \cite{Parker1985} and Rumelhart et al. \cite{Rumelhart1985}, and consists
in updating the weights of the output layer neurons once the erroneous output 
has been obtained, and then, propagating the succesive weight layers back to 
the input layer.

@@

  %[pedro] ya están los resultados de de tabla:results7 para MP5, LR, KNN, SVM.
  % faltan AUN algunas ejecuciones de los de MLP (actualizo con los resultados últimos media+-stdev)
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method   & Time (sec.)         & MAE     & RMSE    & RAE (\%)  & RRSE (\%)      \\
\hline
  M5P     & 7.77 $\pm$ 1.15     & 117.78  & 260.05  & 18.51     & 17.00  \\
\hline
  LR      & 41.72 $\pm$ 8.41    & 120.29  & 252.91  & 18.91     & 16.54   \\
\hline
  SVM     & 1652.20 $\pm$ 283.50& 109.30  & 251.16   & 17.18    & 16.42   \\
\hline
  kNN     & 0.03 $\pm$ 0.01     & 293.98  & 1071.52  & 46.21    & 70.06   \\
\hline
  MLP     & 3595.24 $\pm$ 97.50 & 691.84 $\pm$ 82.71   & 1619.92 $\pm$ 91.67  & 108.74 $\pm$ 13.00   & 105.91 $\pm$ 5.99   \\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different 
forecasting methods on the dataset with 7 variables per book.}}
\label{tabla:results7}
\end{table*}

>>>>

%% Many companies must face, as one of the most difficult tasks to
%% accomplish, new product sales estimation, since in many cases no
%% historical data to serve as guide is available. 
%% Moreover, some of them lack the knowledge about forecasting methods
%% and they can only make decisions based on the expert sales
  %% managers. 
% Eliminado esto.
When a new book is published the publishing house faces the problem of
how many books should be printed. Printing too many is the main issue,
since it implies a loss of investment due to inventory excess. That is
why in this paper we are tackling the problem or predicting sales to %FERGU: The problem ON predicting, no?
print the right amount of books, doing so even before the book has
reached shelves, which is when printing occurs. 
%Thus, making inaccurate predictions may lead to erroneous decisions that result in excess production that will not be sold, or even to a production deficit.
%That is the publishing roll problem, in which publishing companies must estimate the number of volumes printed, taking care not to print more than they actually end up selling. Thus, an automatic prediction of book sales to estimate the publishing roll would be helpful for publishers.
% In the literature, different methods of sales prediction, mainly for
% the fashion industry are proposed. 
% Esto no pega nada en el abstract - JJ
%In these works, when sales are stable with a clear trend over time, the classical methods are a good choice. 
%However, in the case of new products, such as a new book publishing, classical methods do not work properly.
%In this paper, a rule-based decision method is proposed to address the
%problem of predicting the publishing roll.  
% It's not proposed. It just obtained the best result with WEKA. - JJ 
% Publishing roll? ¿Qué es? - JJ
%[Pedro] en la traducción de términos Antonio propone traducirlo como "print run". Lo pongo así.
In this paper, which works with data on published books for several years in
Spain, we first apply a data visualization and preprocessing strategy to find
out what are the relevant variables in the prediction of sales, and
then use standard data mining software to predict sales, and from them
deduce print-run, based on those variables. Our work discovers which
are the most relevant variables when predicting sales, and is
eventually able to predict sales with remarkable accuracy. In fact,
this method has been validated by the company that provided the data 
and incorporated in a business intelligence tool for publishing houses,
since the obtained models provide information on the decision process and
does not require human intervention either for the operation or for
interpretation.
\end{abstract}

@@

However, accurately using a predictive tool is a difficult task as
book sales are influenced by various factors that make
them fluctuate and usually they might be not controllable and
sometimes unknown. 
Some have to do with decisions on purchases, others with freight %FERGU: El Some have to do me suena raro
traffic, and others with the distribution strategy \cite{Little1998}.

@@

The rest of this paper is structured as follows: next, 
Section \ref{sec:soa} presents a comprehensive review of the
approaches found in the bibliography related to the prediction of
sales from product characteristics. 
Then, Section \ref{sec:problem} describes the 
problem of how many books should be printed when a new book is published, 
        % no es el problema de publicación, es el problema de venta
        % de libros sin publicar. Habrá que buscar un nombre - JJ
        %[Pedro] cierto, lo cambio, aunque me ha quedado un nombre muy largo  :)
 followed by Section \ref{sec:methodology} where the
experimental setup and the methodology considered in the study is
presented.  %FERGU: mejor described para no repetir
Section \ref{sec:experiments} reports and analyzes the obtained results with a 
real data set. Finally, conclusions and future work are presented in Section
\ref{sec:conclusionsAndFutureWork}.

%********************************************************************************
\section{Sales forecasting. State of the art} %FERGU: State of the art on sales forecasting?
\label{sec:soa}

@@

Specifically, using time series prediction methods \cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990} 
is perhaps the most used technique to tackle the sales forecasting problems, %FERGU: terminar esta frase con punto en vez de coma para que no sea larga
the efficiency of these techniques depends largely on the field of application 
and the problem data as they require a large amount of data for predicting 
sales of new products are not the most suitable for this task \cite{ChingChin2010}.

@@

  %[pedro] sobre la industria editorial no hay trabajos sobre predicción de ventas.
  % Lo habitual ha sido usar el conocimiento de expertos para realizar predicciones 
  %  o aconsejar acerca de la cantidad de libros a imprimir.
  % Lo más parecido que he encontrado son dos trabajos (uno en realidad) de Moon et al. 
  %  sobre "Use Blog Information As Book Sales Prediction":
  %     Moon2010ICSSSM
  %     Moon2010ICEC
Recently, some works propose \cite{Moon2010ICSSSM,Moon2010ICEC} analyzing 
relationships between on-line information and book sales.
Specifically, authors propose using the number of blog references as an indicator 
of book sales.
Different sales patterns are observed by analyzing data obtained.
In any case, in this research, historical data from published books is used, %FERGU: a qué research se refiere? A la nuestra o a la de la referencia? Dejarlo más claro, por si acaso
and the proposed methodology can not be usable in the problem of unpublished-books 
sales prediction.

@@

Some authors have faced the problem of forecasting sales of new products using 
different data mining methods \cite{Hammond1990,Chang2009,ChingChin2010,Thomassey2012,Xia2012}. 
Thomassey et al \cite{SThomassey2014} propose using a clustering method and 
decision trees for sales forecasting in textile-appared fashion industry, %FERGU: appared? apparel, creo
a very similar issue to the new book publishing problem.
The same problem was previously faced by Xia et al \cite{Xia2012} using a 
forecasting method based on extreme learning machine with adaptive metrics of inputs.
Complexity of this problem is due to the lack of historical data, short lifetime 
of the large number of items, and due to the influence of variables such as 
promotions, fashions, or economic environment \cite{Thomassey2012,Xia2012,SThomassey2014}.

  %[Pedro] otro caso muy similar es el paper de ChingChin2010 sobre:
  % New tea product
  % New cosmetic product
  % New soft drink product
In \cite{ChingChin2010}, a decision-support system for new product sales %FERGU: The work of Chinchin et al.?
forecasting is proposed to solve three real-world sales forecasting problems 
involving new tea, cosmetic, and soft drink products taking into account 
quantitative variables. 
In this study, it is assumed that products are classified based on their sales 
pattern so that products in the same class would have similar sales pattern. %FERGU: "_a_ similar sales pattern", mejor? 
However, as the authors state, proposed system can not deal with qualitative 
date related to the products, and even more real-world cases, such as consumer 
electronics and fashion products, should be examined, as these industries 
introduce new products every season.

  %[Pedro] otro caso a comentar es el paper de Chang2009 sobre: 
  % sales forecasting in printed circuit board industry.
In those cases where historical data is available, classical time series 
forecasting methods can be applied, such as in \cite{Chang2009}, where a hybrid 
model integrating K-mean and fuzzy neural networks to forecast the future sales 
of a printed circuit board is proposed.
A similar method is proposed by Chern et al \cite{Chern2015}, who analyze 
historical data along online reviews, reviewer characteristics and review 
influences to understand how electronic word-of-mouth affects product sales. 
Proposed method is suitable in those sales forecasting problems with abundant %FERGU: _The_ proposed method? 
online reviews and historical data.

@@

In the case of already published books, available historical data might help 
to generate predictive models.
However, in the case of new books there is no historical data to define patterns, 
and only some descriptive data about the new book is available. %FERGU: data es plural. is->are
In these cases not any forecasting method can be used \cite{Madsen2008,ChernWSF15}.

An additional issue is the difficulty to compare our model with classical 
forecasting methods, such as time series prediction methods, since books 
do not have specific sales time series.

Throughout this research, we collaborated with the company Trevenque Editorial, %\footnote{{\tt http://editorial.trevenque.es}}, 
a company that provides management systems and services for libraries, publishers 
and distributors.

Trevenque company, whose expert manager advised this research, provided %FERGU: los párrafos anteriores son un poco dispersos, puedes quitar los puntos y aparte y agruparlos por temas (por ejemplo, todo lo de Trevenque debería de ir en un párrafo)
the initial data set consisting of 3159 books.
In this data set, descriptive information for each book includes price, 
selling points, matter, publisher, sales, returns, among other information.
Table \ref{tabla:paramsOrig50} shows the original set of parameters describing 
each book.

@@

There are several issues inherent to the problem of predicting sales of new 
products: the limitation on the amount of data available, the application of 
different methods and choose the most suitable of them.
In addition, there is no a standard methodology to solve the general problem 
of sales forecasting. %FERGU: hacer más hincapié de esto en la intro entonces
Usually, a preliminary analysis of the data is carried out to eliminate those 
variables that describe the product but do not provide useful information during 
the prediction process.

@@

Thus, in this study there are three main stages (see Figure \ref{fig:stages} %FERGU: there are->we propose
for details): 
\begin{itemize}

@@

  \item  Then, several forecasting methods have to be tested. In this stage 
  different forecasting methods are used to obtain sales forecasts from the 
  data provided.

@@

Finally, in the literature different error measures can be found to report 
the results obtained using the prediction methods \cite{ChingChin2010,Madsen2008}. 
Those error measurements are also called error functions or cost functions. 
%One of the most commonly used is the mean absolute error (see equation \ref{eq:MAE}).
In any case, we recommend using widely accepted standard 
equations\footnote{http://www.gepsoft.com/gxpt4kb/Chapter10/Section3/Introduction.htm} %FERGU: mejor tratar esto como una referencia, ya que es un texto
in order to compare obtained results with those presented in other research 
papers using other methods.
That is why different standard error measurements (Equations \ref{eq:MAE} to \ref{eq:RRSE}), 
implemented in tools like Weka\footnote{http://wiki.pentaho.com/display/DATAMINING} \cite{Witten2011} 
or R\footnote{https://www.otexts.org/fpp/2/5} \cite{Hyndman2013}, are proposed.

Specifically, in order to compute the forecasting errors of the different methods, %FERGU: quitar este salto de linea y unirlo al párrafo de arriba
Mean absolute error (MAE), Root mean squared error (RMSE), Relative absolute 
error (RAE) and Root relative squared error (RRSE) have been selected:

@@

This method is usually applied to analyze data as similar items tend to be 
mapped close together, while those items dissimilar, are mapped apart.
Also, the SOM graph represents and highlight very clearly those regions (clusters) 
with high training sample concentration and fewer where the samples are scarce. %FERGU: mencionarlo en la intro

As stated in Section \ref{sec:problem}, an expert sales manager collaborated in 
this research in the stage of data analysis. Thus, the process was as follows:
\begin{itemize}
  \item First, the expert removed superfluous variables, and dimensionality was 
  reduced from 50 to 43 inputs.
  \item Then, the expert, using his knowledge and the information obtained 
  analyzing the SOM results, removed some inputs, reducing the number of 
  variables describing a book from 43 to 13.
  \item The company asked to include the information about \emph{editorial} 
  and \emph{materia}. Thus, in a new iteration, taking into account the expert's %FERGU: materia no existe en inglés. Subject?
  advice and the information obtained analyzing the SOM results, the number of 
  inputs was decreased to 7.
  \item In a third step, several forecasting methods were used on the obtained 
  dataset, and the best was chosen to obtain an accurate predicting model.
  \item Finally, some information about the new book, such as \emph{author}, 
  although not included in the obtained models, was taken into account by 
  the expert sales manager to modify the forecasted results. 
\end{itemize}

@@

More specifically, in a first step, the expert analyzed the 50 input variables 
describing each book to remove those that were superfluous.
Table \ref{tabla:params43} shows the set of variables describing a book 
(43 total inputs) that the expert manager determined as non-superfluous or 
non-redundant.

@@

\hline
\end{tabular}
\end{center}
\end{table}
%FERGU: para ahorrar espacio se puede hacer la tabla inversa: variables que se han quitado (las 7)
Then, after analyzing the original dataset using the SOM to select the best %FERGU: parametros o framework SOM usados?
variables to be considered, and taking into account the knowledge of the company 
experienced manager, 13 inputs were considered. 
Figure \ref{fig:som43} shows the initial analysis of dataset using the total 
of 43 descriptive inputs per book.
Table \ref{tabla:params13} shows the set of variables describing a book after 
the second analysis.
	% esta gráfica no aporta nada, ni la siguiente tampoco. No se puede
	% colocar en un trabajo en revista  cómo ha ido el entrenamiento, sino
	% datos serios de análisis estadístico de las variables. 
	% [Pedro] sí, estoy de acuerdo. Esto va con el ISSUE #6
\begin{figure}[!h] 
\begin{center}
\begin{tabular}{c}
  \epsfig{file=som43vars.eps,width=11cm} \\
  \epsfig{file=som43umatrix.eps,width=5cm}
\end{tabular}
\caption{\small{Initial data analysis, using 43 descriptive variables per book, %FERGU: la figura está en español, pero ya lo sabréis :P
using SOM.}}
	% Cojollos, ¿qué trabajo os cuesta poner esto en inglés directamente? - JJ
	% [Pedro] sí, si estoy de acuerdo... hay días que me "sale" el texto en inglés,
	% pero hay días que soltar la parrafada en español me resulta más fácil    :/
        % Sería más bien exploratory data analysis o data visualization. 
        % Un gráfico no es un análisis. Y pon las cosas cortas en inglés, hombre - JJ
\label{fig:som43}
\end{center}
\end{figure}

@@

Finally, after analyzing the dataset with 13 descriptive inputs per %FERGU: describis los resultados antes de explicar que volveis a hacer SOM
book, and paying attention to the company experienced manager's
recommendations, 7 inputs were considered; specifically, variables
\emph{EDITORIAL} and \emph{MATTER} were included, while %FERGU: vale, no useis MATTER, usad mejor SUBJECT (MATTER es materia de física, creo xD)
\emph{TOTAL DEVOLUTIONS, REPRINTS, TOTAL SELLING POINTS FIRST YEAR,
  NUMBER OF REPRINTS, TOTAL DEVOLUTIONS FIRT YEAR, TOTAL DISTRIBUTED FIRST YEAR,
  WEEKS ON SALE, PRINT-RUN} were discarded.  
	% Hay que aportar datos de por qué se hizo esto. ¿Análisis de planos?
	% ¿Análisis de varianza? - jj
	% [Pedro] En cuanto estén los SOM definitivos lo añadimos. Está relacionado con el ISSUE #6
Figure \ref{fig:som13} shows the initial analysis of dataset using the SOM on 
the total of 13 descriptive inputs per book.
This, along with the expert manager knowledge determined the final 7 inputs 
to be considered.
Table \ref{tabla:params7} shows the final set of variables describing a book, 
taking into account the company experienced manager knowledge.

\begin{figure}[!h] 
\begin{center}
\begin{tabular}{c}
  \epsfig{file=som13vars.eps,width=11cm} \\
  \epsfig{file=som13umatrix.eps,width=5cm}
\end{tabular}
\caption{\small{Analysis of the initial data, using 13 descriptive variables per book, using the SOM.}} % Análisis de los datos iniciales, usando 13 variables descriptivas por libro, utilizando el SOM.}} %FERGU: teniais esto en español, lo he traducido al inglés :)
% describir de forma más precisa: visualización usando UMatrix de... - JJ
% ¡y usar nombres en inglés para las variables! - JJ
%[pedro] es el siguiente arreglo que le haré mañana al paper    ;)
\label{fig:som13}
\end{center}
\end{figure}

@@

However, as in the case of new books only some descriptive data is available %FERGU: data es plural. is->are
(compared to those cases in which historical data on sales of published books 
is available), not all forecasting methods can be used in this specific problem.

Thus, in this research five forecasting methods, based on the literature 
review in the introduction 
\cite{Madsen2008,ChingChin2010,Thomassey2012,Xia2012,SThomassey2014}, have been used. 
Well known forecasting methods implemented in the Weka tool
\cite{Hall2009,Witten2011} have been chosen, as these methods are
widely known, and could be very helpful for practitioners to reproduce
experiments and even to solve similar sales prediction problems using
these methods. % eliminado el pie de página, es mejor usar referencias - JJ

Specifically, the following forecasting methods are proposed:
\begin{itemize}

@@

 % weka.classifiers.functions.SMOreg
 %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/SMOreg.html
 \item \emph{Support Vector Machine for Regression (SVM)}:
Support vector machine (SVM) \cite{Cortes1995,Shevade1999} method is based on  
statistical learning theory and has successfully used in classification and  
regression problems \cite{Cao2003,Jari2008}.

In classification problems the algorithm searches for an optimal hyperplane 
that separates two classes, maximizing the margin between two classes. 
In the case of regression the algorithm chooses a hyperplane close to as many 
of the data points as possible, minimizing the sum of the distances from 
the data points to the hyperplane. 
In both cases, the hyperplane is defined by a subset of training set samples 
(called support vectors).
%This method works well even if the space is highly dimensional and the problem is not linearly separable.

 % weka.classifiers.lazy.IBk 
 %		http://weka.sourceforge.net/doc.dev/weka/classifiers/lazy/IBk.html
 \item \emph{k-Nearest Neighbours (kNN)}: 
The kNN \cite{Aha1991,Mitchell1997} method is an instance-based classifier in 
which the unknown instances are classified by relating them to the known 
instances using a distance measurement/function (Euclidean, Minkowsky or minimax).

@@

The classification algorithm locates the nearest neighbour in instance space and 
assigns the class of that neighbour to the unknown instance.
In order to improve the robustness of the model, several neighbours can be 
located, assigning the resulting class to an unclassified vector using the 
closest k vectors found in the training set by majority vote.

@@

This kind of artificial neural network is trained using a supervised learning 
technique called back-propagation.
This training method was developed independently by Werbos \cite{Werbos1974}, 
Parker \cite{Parker1985} and Rumelhart et al. \cite{Rumelhart1985}, and consists
in updating the weights of the output layer neurons once the erroneous output 
has been obtained, and then, propagating the successive weight layers back to 
the input layer.

@@

  %[pedro] ya están los resultados de de tabla:results7 para MP5, LR, KNN, SVM.
  % faltan AUN algunas ejecuciones de los de MLP (actualizo con los resultados últimos media+-stdev)
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method   & Time (sec.)         & MAE     & RMSE    & RAE (\%)  & RRSE (\%)      \\
\hline
  M5P     & 7.77 $\pm$ 1.15     & 117.78  & 260.05  & 18.51     & 17.00  \\
\hline
  LR      & 41.72 $\pm$ 8.41    & 120.29  & 252.91  & 18.91     & 16.54   \\
\hline
  SVM     & 1652.20 $\pm$ 283.50& 109.30  & 251.16   & 17.18    & 16.42   \\
\hline
  kNN     & 0.03 $\pm$ 0.01     & 293.98  & 1071.52  & 46.21    & 70.06   \\
\hline
  MLP     & 3595.24 $\pm$ 97.50 & 691.84 $\pm$ 82.71   & 1619.92 $\pm$ 91.67  & 108.74 $\pm$ 13.00   & 105.91 $\pm$ 5.99   \\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different 
forecasting methods on the dataset with 7 variables per book.}}
\label{tabla:results7} %FERGU: es normal que con menos variables tarde más?
\end{table*}
